Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance). The \our on the left side of the table used 256 inducing points } 
	\label{tbl:uci}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{1pt}
	\setlength{\tblw}{0.08\textwidth}

>>>>

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD, lower better). Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}. See \cref{app:uci} for additional tables with comparisons.} 
	\label{tbl:uci}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{1pt}
	\setlength{\tblw}{0.08\textwidth}
